Hydras \& Co.

### 2024-01-09 doc/chapter-primrec.tex
small corrections

@@

\begin{remark}
In the following snippet,  some versions \emph{Alectryon}'s \texttt{Latex} generator  print the \emph{local definition} of $x$ (as the maximum of $2$ and $m$) as a simple \emph{declaration} \texttt{x: nat}.
Thus the proof script is correct, but the three last sub-goals are not correctly displayed, since 
they do not show how the inequalities $2\leq x$ and $m \leq x$ could be inferred by \texttt{lia}.

>>>>

\section{Ackermann function is not primitive recursive}

\label{sect:ack-not-PR}

@@

\begin{remark}
In the following snippet,  some versions of \emph{Alectryon}'s \texttt{Latex} generator  print the \emph{local definition} of $x$ (as the maximum of $2$ and $m$) as a simple \emph{declaration} \texttt{x: nat}.
Thus the proof script is correct, but the three last sub-goals are not correctly displayed, since 
they do not show how the inequalities $2\leq x$ and $m \leq x$ could be inferred by \texttt{lia}.
